\huge Gap formation and stability in non-isothermal disks\\ \Large [2014 CITA Summer Student Program]

### 2014-07-03 poster/poster.tex
updated poster tex

\title{\huge Gap formation and stability in non-isothermal disks}
\author{Min-Kai Lin and Robert Les}
\institute[CITA]{Canadian Institute for Theoretical Astrophysics, 60
  St George Street, Toronto, M5S 3H8, Canada}
%% \date[Sep. 8th, 2009]{Sep. 8th, 2009}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}
  \begin{columns}
    % ---------------------------------------------------------%
    % Set up a column 
    \begin{column}{.49\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth}  % tweaks the width, makes a new \textwidth
          \parbox[t][\columnheight]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content            
            \begin{block}{{\Large Introduction}}
              \justifying
                  {\large              
                    {\bf
                      stuff
                    }
                  }
            \end{block}
            \vfill

            \begin{block}{{\Large The generalized potential vorticity}}
              \justifying

            \end{block}

@@

            \begin{block}{{\Large Linear stability}}
              \justifying

            \end{block}

            \vfill            
            \begin{block}{\Large{Non-linear vortex evolution}}
              \justifying

            \end{block}
          }
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column

@@

            \begin{block}{{\Large Conclusions so far}}\justifying
              {\large{\bf

                }
              }
            \end{block}
          }
          % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column
  \end{columns}
  \vskip1ex
  %\tiny\hfill\textcolor{ta2gray}{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php}}
  %% \tiny\hfill{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php} \hskip1em}
\end{frame}
\end{document}

>>>>

\title{\huge Gap formation and stability in non-isothermal
  disks\\ \Large [2014 CITA Summer Student Program]}
\author{Min-Kai Lin and Robert Les}
\institute[CITA]{Canadian Institute for Theoretical Astrophysics, 60
  St George Street, Toronto, M5S 3H8, Canada}
%% \date[Sep. 8th, 2009]{Sep. 8th, 2009}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}
  \begin{columns}
    % ---------------------------------------------------------%
    % Set up a column 
    \begin{column}{.49\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth}  % tweaks the width, makes a new \textwidth
          \parbox[t][\columnheight]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content            
            \begin{block}{{\Large Introduction}}
              \justifying
                  {\large              
                    {\bf
                    }
                  }
            \end{block}
            \vfill

@@

            \begin{block}{{\Large The generalized potential vorticity}}
              \justifying
              {\bf generalized vortensity profile due to planet for
                different beta. also density profiles.}
            \end{block}

            \vfill

            \begin{block}{{\Large Linear stability}}
              \justifying
                  {\bf plot of growth rate v.s m for different beta,
                    or table. 2D density plot showing development of
                    vortex, for different beta}
            \end{block}
            \vfill
          }
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column

@@

            \begin{block}{\Large{Non-linear vortex evolution}}
              \justifying
                  {\bf `lifetime' plot of m=1 for diff beta, snapshots
                    (before, during, after vortex decay). quote rossby
                  number when vortices in quasi-steady state}
            \end{block}
            \vfill
            \begin{block}{{\Large Conclusions so far}}\justifying
              {\large{\bf

                }
              }
              \vfill
            \end{block}
          }
          % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column
  \end{columns}
  \vskip1ex
  %\tiny\hfill\textcolor{ta2gray}{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php}}
  %% \tiny\hfill{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php} \hskip1em}
\end{frame}
\end{document}
